```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=FALSE, output=FALSE, source = FALSE)
Sys.setenv(ON_workdir = '/home/kabir/offernet/')
```

# All experiments

Here we dump data of all experiments that were run in the period between April 2, 2018 and April 14, 2018. Some of the simulations crashed, some were duplicated with different timeout values, yet the data is preserved (in the report as well as database). From all these only the following experiments are selected to be analyzed further:

|No. | expermentId | Comment |
|:--|:--|:--|
|1 | EXP08-05-12-48-qrNbzW | randomly connected social network of agents, unknown diameter; similarityConnectThreshold = 0.5 |
|2 | EXP08-09-05-27-BmCFH6 | same as above |
|3 | EXP08-10-01-33-JYSw5Z | same as above |
|4 | EXP08-11-12-58-3BvMSL | pre-generated smallWorld social network of agents with known diameters < 10; similarityThreshold = 0.9 |
|5 | EXP08-12-11-17-5tvhCK | pre-generated smallWorld social network of agents with known diameters < 10; different similarity search thresholds |

<!--#### variables: -->
```{r get-experiment-info, results = 'asis', eval=TRUE}
library(elastic)
library(jsonlite)
library(knitr)
library(kableExtra)
library(plyr)
library(stringi)

conn <-connect(es_port = 9200)
template <- '{
    "query": {
        "bool": {
          "must": [
            {"exists" : { "field" : "experimentId" }}
          ],
          "must_not": [
            {"exists" : { "field" : "simulationId"}}
          ]
        }
    },
    "sort": [
      {
        "@timestamp": {
          "order": "asc"
        }
      }
    ]
}'
query <- sprintf(template)
source=c('experimentId','@timestamp','agentNumbers','chainLengths','randomWorksNumberMultipliers','maxDistances','similaritySearchThresholds', 'similarityConnectThreshold')
experiment.result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=1000)$hits$hits
conn<-NULL
experiment.df <- experiment.result[,-c(1:5)]
vars=sapply(strsplit(colnames(experiment.df), split='.', fixed=TRUE), function(x) (x[2]))
colnames(experiment.df) <- vars
colnames(experiment.df)[3] <- 'timestamp' # for some reason this is needed when running from bookdown...
refcols <- c("experimentId", "timestamp")
experiment.df <- experiment.df[, c(refcols, setdiff(names(experiment.df), refcols))]
# print Experiment data
cat(paste('## All experiments in database \n\n'))
kable(experiment.df) %>%
  kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
    scroll_box(height = NULL, width = '1300px',
        box_css = "border: 1px solid #ddd; padding: 5px; ", extra_css = NULL)
    #column_spec(0:ncol(experiment.df),width="10em") 
    #add_header_above(c("labels"=5))

experimentIds = experiment.df$experimentId
for (experimentId in experimentIds) {
  cat(paste('## ',experimentId,'\n\n'))
  cat(paste('### All simulations of experiment \n\n'))
  conn <-connect(es_port = 9200)
  template <- '
        {
            "query": {
                "bool": {
                  "must": [
                    {"exists" : { "field" : "experimentId" }},
                    {"exists" : { "field" : "simulationId" }},
                    {"match_phrase": {
                      "experimentId": "%s"
                    }}
                  ],
                  "must_not": [
                    {"exists" : { "field" : "timeout_ms" }}
                  ]
                }
            },
            "sort": [
              {
                "@timestamp": {
                  "order": "asc"
                }
              }
            ]
        }  
  '

  query <- sprintf(template, experimentId)
  source=c('simulationId','randomWorksNumberMultiplier', 'similaritySearchThreshold','similarityConnectThreshold','maxDistance','agentNumber','@timestamp','chainLength')
  exp.result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=10000)$hits$hits
  conn<-NULL
  
  cat('\n\n')
  cat('\n\n')
  if (is.list(exp.result) & length(exp.result) != 0) {
    exp.df <- exp.result[,-c(1:5)]
    vars=sapply(strsplit(colnames(exp.df), split='.', fixed=TRUE), function(x) (x[2]))
    index <- match('@timestamp',vars)
    vars[index] <- 'timestamp'
    colnames(exp.df) <- vars
    refcols <- c("simulationId", "timestamp")
    exp.df <- exp.df[, c(refcols, setdiff(names(exp.df), refcols))]
    
    template <- '
        {
            "query": {
                "bool": {
                  "must": [
                    {"exists" : { "field" : "experimentId" }},
                    {"exists" : { "field" : "simulationId" }},
                    {"exists" : { "field" : "timeout_ms" }},
                    {"match_phrase": {
                      "experimentId": "%s"
                    }}
                  ]
                }
            },
            "sort": [
              {
                "@timestamp": {
                  "order": "asc"
                }
              }
            ]
        }
    '
  query <- sprintf(template, experimentId)
  source=c('simulationId','timeout_ms')
  timeout.result <- Search(index="filebeat-*", body=query, source = source, asdf=TRUE, size=10000)$hits$hits
  conn<-NULL
  sims.df <- exp.df
  if (is.list(timeout.result) & length(timeout.result) != 0) {
    timeouts.df <- timeout.result[,-c(1:5)]
    vars=sapply(strsplit(colnames(timeouts.df), split='.', fixed=TRUE), function(x) (x[2]))
    colnames(timeouts.df) <- vars
    sims.df <- merge(x = exp.df, y = timeouts.df, by = "simulationId", all = TRUE)
  }

  ee <- kable(sims.df) %>%
    kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
      scroll_box(height = NULL, width = '1300px',
        box_css = "border: 1px solid #ddd; padding: 5px; ", extra_css = NULL)
      #column_spec(0:ncol(experiment.df),width="10em") 
      #add_header_above(c("labels"=5))
  print(ee)

  cat(paste('### Running time of each simulation by method \n\n'))
  simulationIds = sims.df$simulationId
  
  for (simulationId in simulationIds) {1
      cat(paste('#### ',simulationId, '\n\n'))
      cat(paste('##### simulationParameters \n\n'))
      
      params <- sims.df[which(sims.df$simulationId == simulationId),]
      params <- params[,-c(1,3)]
      rownames(params) <- c()
      simp <- kable(params) %>%
        kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') #%>%
      print(simp)
      
      for_sum.df <-data.frame()
      for_sum.df <- params
      for_sum.df$experimentId <- experimentId
      for_sum.df$simulationId <- simulationId

      conn <-connect(es_port = 9200)
      template <- '
            {
              "_source": false, 
              "query": {
                "match_phrase": { "simulationId" : "%s" }},
              "aggs": {
                "group_by_method": {
                  "terms": {
                    "field": "method.keyword"
                  },
                  "aggs": {
                    "group_by_method": {
                      "terms": {
                        "field": "method.keyword",
                        "order": {
                          "avg_wallTime_ms": "desc"
                        }
                      },
                      "aggs": {
                        "sum_wallTime_ms": {
                          "sum": {
                            "field": "wallTime_ms"
                          }
                        },
                        "avg_wallTime_ms": {
                          "avg": {
                            "field": "wallTime_ms"
                          }
                        }
                      }
                    }
                  }
                }
              }
            }      
      '

      query <- sprintf(template, simulationId)
      sim.result <- Search(index="filebeat-*", body=query, asdf=TRUE, size=10000)
      sim.df <- sim.result$aggregations$group_by_method$buckets$group_by_method.buckets
      methods.df <- ldply(sim.df, data.frame)
      conn<-NULL
      func <- function(z) if (is.numeric(z)) sum(z) else ''
      sumrow <- as.data.frame(lapply(methods.df, func))      
      sumrow$avg_wallTime_ms.value <- ''
      sumrow$key <- "Total"
      for_sum.df$time_ms <- sumrow$sum_wallTime_ms
      for_sum.df$processes <- sumrow$doc_count
      last_row <- nrow(methods.df) +1
      m <- kable(rbind(methods.df,sumrow),format.args = list(decimal.mark = '.', big.mark = ",")) %>%
        kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
        row_spec(last_row, bold = TRUE)
          #column_spec(0:ncol(experiment.df),width="10em") 
          #add_header_above(c("labels"=5))
      print(m)
      
      keyword <- 'foundCycle'
      cat(paste('#####  Found cycles \n\n'))
      
      conn <-connect(es_port = 9200)
      template <- '
            { 
              "query": {
                "bool": {
                  "must": [
                    { "match_phrase": {
                      "simulationId": "%s"
                      }
                    },
                    { "bool": {
                      "should": [
                        { "match": {
                          "keyword": "%s"
                        }}
                      ]
                    }}
                  ]
                }
              }
            }
  '

      query <- sprintf(template, simulationId, keyword)
      cycle.result <- Search(index="filebeat-*", body=query, asdf=TRUE, size=10000)
      cat(paste("Number of cycles found: ", cycle.result$hits$total),'\n\n')
      for_sum.df$foundCycles <- cycle.result$hits$total
      blockNo <- stri_rand_strings(1, 10, '[A-Z]')
      full_query <- sprintf("%s %s", '     GET /filebeat-*/_search', query)
      tooltip <- "To be used to extract graph from ElasticSearch and visualize via OfferNet visualization engine (given proper access permissions)"
      cat(paste('<button class="btn btn-primary" data-toggle="collapse" data-target="#',blockNo,'"> Show/Hide ',keyword,' query </button> \n <div id="',blockNo,'" class="collapse" >  \n',sep=''))
        cat(paste(full_query,'\n'))
        cat('\n</div>\n')
        
      keyword <- 'foundPath'
      cat(paste('#####  Found paths \n\n'))
      
      conn <-connect(es_port = 9200)
      template <- '
            { 
              "query": {
                "bool": {
                  "must": [
                    { "match_phrase": {
                      "simulationId": "%s"
                      }
                    },
                    { "bool": {
                      "should": [
                        { "match": {
                          "keyword": "%s"
                        }}
                      ]
                    }}
                  ]
                }
              }
            }
  '

      query <- sprintf(template, simulationId, keyword)
      path.result <- Search(index="filebeat-*", body=query)
      cat(paste("Number of paths found: ", path.result$hits$total),'\n\n')
      for_sum.df$foundPaths <- path.result$hits$total
      blockNo <- stri_rand_strings(1, 10, '[A-Z]')
      full_query <- sprintf("%s %s", '     GET /filebeat-*/_search', query)
      cat(paste('<button class="btn btn-primary" data-toggle="collapse" data-target="#',blockNo,'"> Show/Hide ',keyword,' query </button> \n <div id="',blockNo,'" class="collapse">  \n',sep=''))
            cat(paste(full_query,'\n'))
        cat('\n</div>\n')        

      #cat(paste('#### Sumary of simulation','\n\n'))
      
      #sum <- kable(for_sum.df,format.args = list(decimal.mark = '.', big.mark = ",")) %>%
      #  kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') #%>%
          #column_spec(0:ncol(experiment.df),width="10em") 
          #add_header_above(c("labels"=5))
      #print(sum)
    
    
    if (!exists('summary.df')) {
      summary.df <- for_sum.df
    } else{
      summary.df <- rbind.fill(summary.df, for_sum.df)
    }
    
  }
}


timeout.result <-NULL
experiment.result <-NULL
exp.result <-NULL

}

cat(paste('## Summary or running times \n\n'))
refcols <- c("experimentId", "simulationId", "timestamp")
summary.df <- summary.df[, c(refcols, setdiff(names(summary.df), refcols))]
summary <- kable(summary.df,format.args = list(decimal.mark = '.', big.mark = ",")) %>%
  kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
    scroll_box(height = NULL, width = '1300px',
      box_css = "border: 1px solid #ddd; padding: 5px; ", extra_css = NULL)
    #column_spec(0:ncol(experiment.df),width="10em") 
    #add_header_above(c("labels"=5))
print(summary)
```