--- 
title: "Tidy experiment with well distributed properties -- 1"
author: "Kabir Veitas (kabir@singularitynet.io)"
date: "`r Sys.Date()`"
bibliography: book.bib
documentclass: book
github-repo: singnet/offernet
link-citations: yes
site: bookdown::bookdown_site
biblio-style: apalike
url: http\://seankross.com/bookdown-start/
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=FALSE, output=FALSE, source = FALSE)
Sys.setenv(ON_workdir = '/home/kabir/offernet/')
```

```{r init}
#install.packages("jsonlite")
#install.packages("kableExtra")
#install.packages("ggplot2")
#install.packages('elastic')
library(elastic)
library(jsonlite)
library(knitr)
library(kableExtra)
library(plyr)
library(stringi)
```

# Introduction

```{r experiment-description, results = 'asis', eval=TRUE}
selectedExperiments <- c(
'EXP10-02-01-04-YQvrhC',
'EXP10-03-10-34-Lfip5F',
'EXP10-03-11-06-mTThJr', 
'EXP10-04-01-28-KKABTK', 
'EXP10-04-11-00-6NwhDL', 
'EXP10-05-01-29-BHt6a5',
'EXP10-05-10-28-Z7PYyS',
'EXP10-05-02-12-uUGIa6',
'EXP10-06-01-49-jZTN76')

descriptions <- c(
'agentNumbers=[400] : chainLengths=[10, 20] : randomWorksNumberMultipliers=[1, 2] : maxDistances=[5, 10, 30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld]; rest of simulations with 400 agents...',
'agentNumbers=[800] : chainLengths=[5, 10, 20] : randomWorksNumberMultipliers=[1, 2] : maxDistances=[5, 10, 30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld]; rerunning with 800 agents...',
'agentNumbers=[800] : chainLengths=[5] : randomWorksNumberMultipliers=[1] : maxDistances=[30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld]; finishing 800 agent simulations with 1 randomWork after crash...',
'agentNumbers=[800] : chainLengths=[5, 10, 20] : randomWorksNumberMultipliers=[2] : maxDistances=[5, 10, 30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld] : message=[800 agent simulations with 2 randomWorksNumbers...]',
'agentNumbers=[800] : chainLengths=[5, 10, 20] : randomWorksNumberMultipliers=[2] : maxDistances=[10, 30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld]; repeating after crash', 
'agentNumbers=[800] : chainLengths=[5, 10, 20] : randomWorksNumberMultipliers=[2] : maxDistances=[10, 30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld]; another crash -- putting what was left, more data should not harm...',
'gentNumbers=[800] : chainLengths=[5] : randomWorksNumberMultipliers=[2] : maxDistances=[30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld]; finishing 800 agent simulation with maxDistance=30 and chainLength=5 -- after graph database restart, which stopped the repeated crashing (!)',
'agentNumbers=[800] : chainLengths=[10, 20] : randomWorksNumberMultipliers=[2] : maxDistances=[5, 10, 30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld] : message=[Rerunning 800 agent simulations with 2 randomWorksNumbers and 10,20 chainLenghts....]',
'agentNumbers=[800] : chainLengths=[10, 20] : randomWorksNumberMultipliers=[2] : maxDistances=[30] : similaritySearchThresholds=[1] : similarityConnectThresholds=[0.9] : graphTypes=[random, smallWorld] : finishing the previous simulation with 800 agents.')
```

|No. | expermentId | Comment |
|:--|:--|:--|
|1 | `r selectedExperiments[1]` | `r descriptions[1]` |
|2 | `r selectedExperiments[2]` | `r descriptions[2]` |
|3 | `r selectedExperiments[3]` | `r descriptions[3]` |
|4 | `r selectedExperiments[4]` | `r descriptions[4]` |
|5 | `r selectedExperiments[5]` | `r descriptions[5]` |
|6 | `r selectedExperiments[6]` | `r descriptions[6]` |
|7 | `r selectedExperiments[7]` | `r descriptions[7]` |
|8 | `r selectedExperiments[8]` | `r descriptions[8]` |
|9 | `r selectedExperiments[9]` | `r descriptions[9]` |

<!--#### variables: -->
```{r get-experiment-info, results = 'asis', eval=TRUE}

#defining a function to be used somewhere in the end of the document...
scatterplot <- function(data, xstr,ystr, sizestr, colorstr, titlelab, ylab,xlab) {
  gg <- ggplot(data, aes_string(x=xstr, y=ystr, color=colorstr)) + 
    geom_point(aes_string(size=sizestr, color=colorstr)) + 
    geom_smooth(method="loess", se=F) + 
    #xlim(c(0, 0.1)) + 
    #ylim(c(0, 500000)) + 
    labs(title=titlelab, 
         y=ylab, 
         x=xlab, 
         size=sizestr,
         color=colorstr)
}


# need to run this in order to get
# PUT _all/_settings
# {
#     "index" : {
#         "max_result_window" : "10000000"
#     }
# }

x<-1
for (experimentId in selectedExperiments) {
  cat(paste(experimentId))
  cat(paste('   \n\n'))
  cat(paste('# Experiment ',x, '\n\n'))
  cat(paste(descriptions[x],'\n\n'))
  x<-x+1
  cat(paste('## Experimental set up','\n\n'))
  conn <-connect(es_port = 9200)
  template <- '{ 
    "query": {
      "bool": {
        "must": [
          { "match_phrase": {
            "experimentId": "%s"
            }
          }
        ],
        "must_not": [
          { "exists": { "field": "simulationId" } }
        ]
      }
    }
  }'
  query <- sprintf(template, experimentId)
  source=c('experimentId','agentNumbers','chainLengths','randomWorksNumberMultipliers','maxDistances','similaritySearchThresholds ', 'similarityConnectThresholds','graphTypes')
  
  
  result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=10000)$hits$hits
  experiment.df <- result[,-c(1:4)]
  vars=sapply(strsplit(colnames(experiment.df), split='.', fixed=TRUE), function(x) (x[2]))
  colnames(experiment.df) <- vars
  refcols <- c("experimentId", "agentNumbers")
  experiment.df <- experiment.df[, c(refcols, setdiff(names(experiment.df), refcols))]
  experiment.df <- t(experiment.df)
  colnames(experiment.df) <- c('Values')
  
  # print Experiment data
  exp <- kable(experiment.df) %>%
    kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') #%>%
      #column_spec(0:ncol(experiment.df),width="10em") 
      #add_header_above(c("labels"=5))
  print(exp)
  
  
  cat('## Descriptive analysis of each simulation\n\n')
  
  conn <-connect(es_port = 9200)
  template <- '{ 
    "query": {
      "bool": {
        "must": [
          { "match_phrase": {
            "experimentId": "%s"
            }
          },
          { "match" :{
            "keyword": "simulationParameters"
          }},
          { "exists": { "field": "simulationId" } }
        ]
      }
    }
  }'
  query <- sprintf(template, experimentId)
  source=c('simulationId','agentNumber','chainLength','randomWorksNumberMultiplier','maxDistance','similaritySearchThreshold','similarityConnectThreshold','graphType')
  result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=10000)$hits$hits
  
  simulations.df <- result[,-c(1:4)]
  vars=sapply(strsplit(colnames(simulations.df), split='.', fixed=TRUE), function(x) (x[2]))
  colnames(simulations.df) <- vars
  refcols <- c("simulationId", "agentNumber")
  simulations.df <- simulations.df[, c(refcols, setdiff(names(simulations.df), refcols))]
  simulations.df <- simulations.df[order(simulations.df$agentNumber, simulations.df$chainLength, simulations.df$maxDistance, simulations.df$simulationId),]
  # getting rid of the simulation data on which the experiment crashed -- gives error...
  simulations.df <- simulations.df[which(simulations.df$simulationId != "SIM10-03-06-48-cbHp3o--DV"), ]
  simulations.df <- simulations.df[which(simulations.df$simulationId != "SIM10-04-08-48-g9JKkC--DV"), ]
  simulations.df <- simulations.df[which(simulations.df$simulationId != "SIM10-04-03-23-mQeaNs--DV"), ]
  simulations.df <- simulations.df[which(simulations.df$simulationId != "SIM10-05-07-53-XPZNSG--DV"), ]
  simulations.df <- simulations.df[which(simulations.df$simulationId != "SIM10-06-12-38-IqpJHw--DV"), ]

  rownames(simulations.df) <- c()
  
  simulationIds <- simulations.df$simulationId
  
    conn <-connect(es_port = 9200)
    template <- '{    "query": {
            "bool": {
              "must": [
                {"exists" : { "field" : "method" }},
                {"exists" : { "field" : "simulationId" }},
                { "bool": {
                  "should": [
                      {"match_phrase": {
                        "method": "allEdgesByLabel"
                      }},
                      {"match_phrase": {
                        "method": "allVerticesByLabel"
                      }},
                      {"match_phrase": {
                        "method": "similarityEdgesByWeight"
                      }}
                  ]
                }}
              ]
            }
        }}'
    query <- sprintf(template)
    source=c('simulationId','results', 'message', 'method','edgeLabel','vertexType','direction')
    result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=10000)$hits$hits
    
    analysis.df <- result[,-c(1:4)]
    vars=sapply(strsplit(colnames(analysis.df), split='.', fixed=TRUE), function(x) (x[2]))
    colnames(analysis.df) <- vars
    
  
  library(ggplot2)
  
  for (simulationId in simulationIds) {
  
    cat(paste('### ',simulationId,'\n\n'))
    cat(paste('#### simulationParameters \n\n'))
    
    simulation.df <- simulations.df[which(simulations.df$simulationId == simulationId),][,-1]
    rownames(simulation.df) <-c()
    
    for_sum.df <-data.frame()
    for_sum.df <- simulation.df
    for_sum.df$experimentId <-  experimentId
    for_sum.df$simulationId <- simulationId
  
      
    # output simulationParameters
    print(kable(simulation.df) %>%
      kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
        column_spec(1:1,width="20em") %>%
        column_spec(2:ncol(simulation.df),width="15em")
        #add_header_above(c("variables"))
    )
    
    simulationData <- analysis.df[which(analysis.df$simulationId == simulationId),]
    
    # output allEdgesByLabel
    test <- simulationData[which(simulationData$method == 'allEdgesByLabel'),]$results
    if (! identical(test, character(0))) {
      edges.df <- data.frame(fromJSON(simulationData[which(simulationData$method == 'allEdgesByLabel'),]$results))
      names <- colnames(edges.df)
      names <- paste('edges',names,sep="_")
      colnames(edges.df) <- names
      
      edges.df$edges_total <- rowSums(edges.df)
      for_sum.df <- cbind(for_sum.df,edges.df)
      cat('#### allEdgesByLabel\n\n')
      print(kable(edges.df, format.args = list(decimal.mark = '.', big.mark = ",")) %>%
        kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
          column_spec(1:ncol(edges.df),width="5em") 
          #add_header_above(c("labels"=5))
      )
    }
    
    # output allVerticesByType
    test <- simulationData[which(simulationData$method == 'allEdgesByLabel'),]$results
    if (! identical(test, character(0))) {
      vertices.df <- data.frame(fromJSON(simulationData[which(simulationData$method == 'allVerticesByLabel'),]$results))
      names <- colnames(vertices.df)
      names <- paste('vertices',names,sep="_")
      colnames(vertices.df) <- names
      
      vertices.df$vertices_total <- rowSums(vertices.df)
      for_sum.df <- cbind(for_sum.df,vertices.df)
      cat('#### allVerticesByType\n\n')
      print(kable(vertices.df, format.args = list(decimal.mark = '.', big.mark = ",")) %>%
        kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
          column_spec(1:ncol(vertices.df),width="5em") 
          #add_header_above(c("labels"=5))
      )
    }
    
    # output similarityEdgesByWeight
    test <- simulationData[which(simulationData$method == 'similarityEdgesByWeight'),]$results
    if (! identical(test, character(0))) {
        similarity <- data.frame(fromJSON(simulationData[which(simulationData$method == 'similarityEdgesByWeight'),]$results))
        wghts <- as.numeric(substring(unlist(names(similarity)),first = 2))
        frequencies <- as.numeric(similarity)
        similarity.df <- data.frame(weight=wghts,edges=frequencies)
        se <- ggplot(data=similarity.df, aes(x=weight, y=frequencies)) +
          geom_bar(stat="identity", fill="steelblue")+
          geom_text(aes(label=weight), vjust=1.6, color="white", size=3.5)+
          xlab("Weight")+
          ylab("Number of edges")+
          theme_minimal()+
          geom_line()
        
        cat('#### distribution of similarityEdgesByWeight\n\n')
        print(se)
        cat('\n\n')
    }
    
    # plot degreeDistribution items-similarity
    conn <-connect(es_port = 9200)
    template <- '{
            "query": {
                "bool": {
                  "must": [
                    {"exists" : { "field" : "method" }},
                    {"exists" : { "field" : "simulationId" }},
                    {"match_phrase": {
                      "simulationId": "%s"
                    }},
                    {"match_phrase": {
                      "method": "%s"
                    }},
                    {"match": {
                      "vertexType": "%s"
                    }},
                    {"match": {
                      "edgeLabel": "%s"
                    }},
                    { "match": {
                      "direction": "%s"
                    }}
                  ]
                }
            }
        }'
    method <- 'degreeDistribution'
    vertexType <- 'item'
    edgeLabel <- 'similarity'
    direction <- 'out'
    query <- sprintf(template, simulationId, method, vertexType, edgeLabel, direction)
    source=c('simulationId','results', 'message', 'method','edgeLabel','vertexType','direction')
    result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=100)$hits$hits
    
    data <- result[,-c(1:4)]
    vars=sapply(strsplit(colnames(data), split='.', fixed=TRUE), function(x) (x[2]))
    colnames(data) <- vars
  
    degrees <- fromJSON(data$results)
    dgr <- as.numeric(substring(unlist(names(degrees)),first = 2))
    frequencies <- as.numeric(degrees)
    degrees.df <- data.frame(degrees=dgr,frequencies=frequencies)
    
    dd_is <- ggplot(data=degrees.df, aes(x=dgr, y=frequencies)) +
      geom_bar(stat="identity", fill="white", color="black")+
      #geom_text(aes(label=dgr), vjust=1.6, color="black", size=3.5)+
      xlab("Degree")+
      ylab("Count")+
      theme_minimal()
  
    cat('#### Degree distribution of item->similarity->item edges\n\n')
    #print(kable(degrees.df))
    #cat('\n\n')
    print(dd_is)
    cat('\n\n')
  
    # plot degreeDistribution agent-knows
    conn <-connect(es_port = 9200)
    template <- '{
            "query": {
                "bool": {
                  "must": [
                    {"exists" : { "field" : "method" }},
                    {"exists" : { "field" : "simulationId" }},
                    {"match_phrase": {
                      "simulationId": "%s"
                    }},
                    {"match_phrase": {
                      "method": "%s"
                    }},
                    {"match": {
                      "vertexType": "%s"
                    }},
                    {"match": {
                      "edgeLabel": "%s"
                    }},
                    { "match": {
                      "direction": "%s"
                    }}
                  ]
                }
            }
        }'
    method <- 'degreeDistribution'
    vertexType <- 'agent'
    edgeLabel <- 'knows'
    direction <- 'both'
    query <- sprintf(template, simulationId, method, vertexType, edgeLabel, direction)
    source=c('simulationId','results', 'message', 'method','edgeLabel','vertexType','direction')
    result <- Search(index="filebeat-*", source=source, body=query, asdf=TRUE, size=100)$hits$hits
    
    data <- result[,-c(1:4)]
    vars=sapply(strsplit(colnames(data), split='.', fixed=TRUE), function(x) (x[2]))
    colnames(data) <- vars
  
    a_degrees <- fromJSON(data$results)
    dgr <- as.numeric(unlist(names(a_degrees)))
    frequencies <- as.numeric(a_degrees)
    a_degrees.df <- data.frame(degrees=dgr,frequencies=frequencies)
    
    dd_ak <- ggplot(data=a_degrees.df, aes(x=dgr, y=frequencies)) +
      geom_bar(stat="identity", fill="white", color="black")+
      #geom_text(aes(label=dgr), vjust=1.6, color="black", size=3.5)+
      xlab("Degree")+
      ylab("Count")+
      theme_classic()
  
    cat('#### Degree distribution of agent->knows->agent edges\n\n')
    #print(kable(a_degrees.df))
    #cat('\n\n')
    print(dd_ak)
    cat('\n\n')  
    
    cat('#### Runing time by method \n\n')
        conn <-connect(es_port = 9200)
        template <- '
              {
                "_source": false, 
                "query": {
                  "match_phrase": { "simulationId" : "%s" }},
                "aggs": {
                  "group_by_method": {
                    "terms": {
                      "field": "method.keyword"
                    },
                    "aggs": {
                      "group_by_method": {
                        "terms": {
                          "field": "method.keyword",
                          "order": {
                            "avg_wallTime_ms": "desc"
                          }
                        },
                        "aggs": {
                          "sum_wallTime_ms": {
                            "sum": {
                              "field": "wallTime_ms"
                            }
                          },
                          "avg_wallTime_ms": {
                            "avg": {
                              "field": "wallTime_ms"
                            }
                          }
                        }
                      }
                    }
                  }
                }
              }      
        '
  
        query <- sprintf(template, simulationId)
        sim.result <- Search(index="filebeat-*", body=query, asdf=TRUE, size=10000)
        sim.df <- sim.result$aggregations$group_by_method$buckets$group_by_method.buckets
        methods.df <- ldply(sim.df, data.frame)
        if (grepl('–CV',simulationId) | grepl('--CV',simulationId)) {
          # this is centralized simulation therefore we need only these methods:
          methodsToExclude <- c('existsSimilarity', 'connectIfSimilar', 'similarityEdges', 'init')
        } else {
          methodsToExclude <- c('knowsAgent', 'addItemToWork','ownsWork', 'init', 'getWorks')
        }
        methodsInTotal.df <- methods.df[which(!(methods.df$key %in% methodsToExclude)),]
        
        # no need to include analysis methods in calculation of total time spent -- exluding all
        analysisMethods <- c('degreeDistribution','allEdgesByLabel', 'allVerticesByLabel', 'similarityEdgesByWeight', 'checkFoundPaths', 'pathContainsChain')
        for (analysisMethod in analysisMethods) {
          if (analysisMethod %in% methods.df$key) {
            i <- which(methods.df$key == analysisMethod)
            methods.df <- methods.df[-c(i),]
          }
        }
        conn<-NULL
        func <- function(z) if (is.numeric(z)) sum(z) else ''
        sumrow <- as.data.frame(lapply(methodsInTotal.df, func))      
        sumrow$avg_wallTime_ms.value <- ''
        sumrow$key <- "Total"
        
        methods.df$includedInTotal <- ifelse(methods.df$key %in% methodsToExclude, "No", "Yes")
        sumrow$includedInTotal <- ''
        
        extractFromMethods <- function(methods.df, column_name, keyword) {
          index <- which(colnames(methods.df)==column_name)
          values <- methods.df[,c(1,index)]
          values <- t(values)
          rownames(values) <-c()
          names <- as.character(as.vector(values[1,]))
          names <- paste(keyword,names,sep="_")
          colnames(values) <-names
          values <- values[-c(1),]
          data.frame(lapply(values, type.convert), stringsAsFactors=FALSE)
        }
        
        #processes <- extractFromMethods(methods.df,'doc_count','processes')
        #times <- extractFromMethods(methods.df,'sum_wallTime_ms.value','times')
        #for_sum.df <- cbind(for_sum.df,processes)
        #for_sum.df <- cbind(for_sum.df,times)
        
        for_sum.df$sum_wallTime_ms_total <- sumrow$sum_wallTime_ms
        for_sum.df$process_total <- sumrow$doc_count
        last_row <- nrow(methods.df) +1
        m <- kable(rbind(methods.df,sumrow),format.args = list(decimal.mark = '.', big.mark = ",")) %>%
          kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
          row_spec(last_row, bold = TRUE)
            #column_spec(0:ncol(experiment.df),width="10em") 
            #add_header_above(c("labels"=5))
        print(m)
        
        keyword <- 'foundCycle'
        cat(paste('####  Found structures \n\n'))
        cat(paste('#####  Cycles \n\n'))
        
        conn <-connect(es_port = 9200)
        template <- '
              { 
                "query": {
                  "bool": {
                    "must": [
                      { "match_phrase": {
                        "simulationId": "%s"
                        }
                      },
                      { "bool": {
                        "should": [
                          { "match": {
                            "keyword": "%s"
                          }}
                        ]
                      }}
                    ]
                  }
                }
              }
    '
  
        query <- sprintf(template, simulationId, keyword)
        cycle.result <- Search(index="filebeat-*", body=query, asdf=TRUE, size=10000)
        cat(paste("Number of cycles found: ", cycle.result$hits$total),'\n\n')
        for_sum.df$foundCycles <- cycle.result$hits$total
        blockNo <- stri_rand_strings(1, 10, '[A-Z]')
        full_query <- sprintf("%s %s", '     GET /filebeat-*/_search', query)
        tooltip <- "To be used to extract graph from ElasticSearch and visualize via OfferNet visualization engine (given proper access permissions)"
        cat(paste('<button class="btn btn-primary" data-toggle="collapse" data-target="#',blockNo,'"> Show/Hide ',keyword,' query </button> \n <div id="',blockNo,'" class="collapse" >  \n',sep=''))
          cat(paste(full_query,'\n'))
          cat('\n</div>\n')
          
        keyword <- 'foundPath'
        cat(paste('#####  Paths \n\n'))
        
        conn <-connect(es_port = 9200)
        template <- '
              { 
                "query": {
                  "bool": {
                    "must": [
                      { "match_phrase": {
                        "simulationId": "%s"
                        }
                      },
                      { "bool": {
                        "should": [
                          { "match": {
                            "keyword": "%s"
                          }}
                        ]
                      }}
                    ]
                  }
                }
              }
    '
  
        query <- sprintf(template, simulationId, keyword)
        path.result <- Search(index="filebeat-*", body=query)
        cat(paste("Number of paths found: ", path.result$hits$total),'\n\n')
        for_sum.df$foundPaths <- path.result$hits$total
        blockNo <- stri_rand_strings(1, 10, '[A-Z]')
        full_query <- sprintf("%s %s", '     GET /filebeat-*/_search', query)
        cat(paste('<button class="btn btn-primary" data-toggle="collapse" data-target="#',blockNo,'"> Show/Hide ',keyword,' query </button> \n <div id="',blockNo,'" class="collapse">  \n',sep=''))
              cat(paste(full_query,'\n'))
          cat('\n</div>\n')        
  
  
        #cat(paste('#### Summary of simulation','\n\n'))
        
        #sum <- kable(for_sum.df,format.args = list(decimal.mark = '.', big.mark = ",")) %>%
        #  kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
        #    scroll_box(height = NULL, width = '1300px',
        #      box_css = "border: 1px solid #ddd; padding: 5px; ", extra_css = NULL)
    
            #column_spec(0:ncol(experiment.df),width="10em") 
            #add_header_above(c("labels"=5))
        #print(sum)
      
      if (!exists('experiment_summary.df')) {
        experiment_summary.df <- for_sum.df
      } else{
        experiment_summary.df <- rbind.fill(experiment_summary.df, for_sum.df)
      }
  }

      # housekeeping on form_sum.df -- correct types and reorder...

      experiment_summary.df$sum_wallTime_min_total <- experiment_summary.df$sum_wallTime_ms_total /60000
      experiment_summary.df$simulationType <- ifelse(grepl('--DV',experiment_summary.df$simulationId),"Decentralized", "Centralized")

      options(scipen=999)  # turn-off scientific notation like 1e+48
      theme_set(theme_bw())  # pre-set the bw theme.

      experiment_summary.df$agentNumber <- sapply(experiment_summary.df$agentNumber, as.numeric)
      experiment_summary.df$chainLength <- sapply(experiment_summary.df$chainLength, as.numeric)
      experiment_summary.df$similaritySearchThreshold <- sapply(experiment_summary.df$similaritySearchThreshold, as.numeric)
      experiment_summary.df$randomWorksNumberMultiplier <- sapply(experiment_summary.df$randomWorksNumberMultiplier, as.numeric)

      file_name <- paste('./R_data/experiment_',experimentId,'_summary.Rdata', sep="")
      save(experiment_summary.df,file=file_name)

      cat(paste('## Scatterplots of experiment','\n\n'))

      ys <- c('sum_wallTime_min_total')
      colors <- c('simulationType')
      used <- append(ys,colors)
      sizes <- c('foundCycles')
      used <- append(used,sizes)
      remove <- c('randomWorksNumberMultiplier', 'experimentId', 'simulationId','sum_wallTime_ms_total', 'foundPaths', 'chainLength','similaritySearchThreshold','similarityConnectThreshold','maxDistance', 'simulationType')
      used <- append(used, remove)
      xs=names(experiment_summary.df)[!(names(experiment_summary.df) %in% used)]


      # generate permutations of the plots with the above variables
      for (y_str in ys) {
        for (color_str in colors) {
          for (size_str in sizes) {
            for (x_str in xs) {
              print(scatterplot(
                experiment_summary.df,
                x_str,
                y_str,
                size_str,
                color_str,
                paste(x_str, ' vs ',y_str),
                y_str,
                x_str))
            }
          }
        }
      }

      if (!exists('summary.df')) {
        summary.df <- experiment_summary.df
      } else{
        summary.df <- rbind.fill(summary.df, experiment_summary.df)
      }

      rm(experiment_summary.df)

}

cat(paste('  \n\n'))
cat(paste('# Cross analysis of all additional experiments\n\n'))
cat(paste('## Summary data \n\n'))
refcols <- c("experimentId", "simulationId")
summary.df <- summary.df[, c(refcols, setdiff(names(summary.df), refcols))]
summary <- kable(summary.df,format.args = list(decimal.mark = '.', big.mark = ",")) %>%
  kable_styling(bootstrap_options='condensed',full_width = FALSE, position = 'left') %>%
    scroll_box(height = NULL, width = '1300px',
      box_css = "border: 1px solid #ddd; padding: 5px; ", extra_css = NULL)
    #column_spec(0:ncol(experiment.df),width="10em") 
    #add_header_above(c("labels"=5))
print(summary)

#summary.df$sum_wallTime_min_total <- summary.df$sum_wallTime_ms_total /60000
#summary.df$simulationType <- ifelse(grepl('--DV',summary.df$simulationId),"Decentralized", "Centralized")

options(scipen=999)  # turn-off scientific notation like 1e+48
theme_set(theme_bw())  # pre-set the bw theme.

cat(paste('## Scatterplots of all experiments \n\n'))

# housekeeping on summary.df -- correct types and reorder...
#summary.df$agentNumber <- sapply(summary.df$agentNumber, as.numeric)
#summary.df$chainLength <- sapply(summary.df$chainLength, as.numeric)
#summary.df$similaritySearchThreshold <- sapply(summary.df$similaritySearchThreshold, as.numeric)
#summary.df$randomWorksNumberMultiplier <- sapply(summary.df$randomWorksNumberMultiplier, as.numeric)

#summary.df$maxDistance <- sapply(summary.df$maxDistance, as.numeric)
summary.df <- summary.df[order(summary.df$agentNumber),] 


summary.df$simulationType_chainLength <- paste(summary.df$simulationType,'-',summary.df$chainLength)
summary.df$simulationType_foundCycles <- paste(summary.df$simulationType,'-',summary.df$foundCycles)
summary.df$simulationType_similaritySearchThreshold <- paste(summary.df$simulationType,'-',summary.df$similaritySearchThreshold)
summary.df$simulationType_similarityConnectThreshold <- paste(summary.df$simulationType,'-',summary.df$similarityConnectThreshold)
summary.df$simulationType_maxDistance <- paste(summary.df$simulationType,'-',summary.df$maxDistance)
summary.df$simulationType_randomWorksNumberMultiplier <- paste(summary.df$simulationType,'-',summary.df$randomWorksNumberMultiplier)

ys <- c('sum_wallTime_min_total')
colors <- c('simulationType_chainLength','simulationType_similaritySearchThreshold','simulationType_similarityConnectThreshold','simulationType_maxDistance', 'simulationType_randomWorksNumberMultiplier')
used <- append(ys,colors)
sizes <- c('foundCycles')
used <- append(used,sizes)
remove <- c('randomWorksNumberMultiplier', 'experimentId', 'simulationId','sum_wallTime_ms_total', 'foundPaths', 'chainLength','similaritySearchThreshold','similarityConnectThreshold','maxDistance', 'simulationType','simulationType_foundCycles')
used <- append(used, remove)
xs=names(summary.df)[!(names(summary.df) %in% used)]

save(summary.df,file='./R_data/summary_of_all_experiments.Rdata')

for (y_str in ys) {
  for (color_str in colors) {
    for (size_str in sizes) {
      for (x_str in xs) {
        print(scatterplot(
          summary.df,
          x_str,
          y_str,
          size_str,
          color_str,
          paste(x_str, ' vs ',y_str),
          y_str,
          x_str))
      }
    }
  }
}

cat(paste('  \n\n'))
cat(paste('## Regression analysis \n\n'))

library(stargazer)

fitCV <- lm(sum_wallTime_min_total ~ agentNumber +  vertices_total + edges_total  +  chainLength + maxDistance + randomWorksNumberMultiplier, data=summary.df[which(summary.df$simulationType == 'Centralized'),])
fitDV <- lm(sum_wallTime_min_total ~ agentNumber  + vertices_total + edges_total  + chainLength + maxDistance + randomWorksNumberMultiplier, data=summary.df[which(summary.df$simulationType == 'Decentralized'),])
fit <- lm(sum_wallTime_min_total ~ agentNumber + vertices_total + edges_total + factor(simulationType) + chainLength + maxDistance + randomWorksNumberMultiplier, data=summary.df)
stargazer(fitCV,fitDV,fit,type = "html",column.labels = c("Centralized", "Decentralized", "All"))

```