```{r numbers, echo=FALSE}
dataDir='2911856a5e51a2818f44b637cf36418109f37847'
fullPath = paste('/media/data/challprop-working/eln/',dataDir, sep="")
setwd(fullPath)
library(stringr)
Sys.setenv(R_dataDir=fullPath)
file <- "code.version"
connection <- file(description=file, open="r")
codeBase <- scan(file=connection, nlines=1, quiet=TRUE, what=character())

```

Date: `r date()` <br/>
Analysis version ([challprop-analytics](https://bitbucket.org/gbi/challprop-analytics)): {analysis_commitNo} <br/>
Experiment version ([challprop-experiments](https://bitbucket.org/gbi/challprop-experiments)): `r str_sub(dataDir,1,8)` <br/>
Codebase version ([challprop-java](https://bitbucket.org/gbi/challprop-experiments)): `r str_sub(codeBase,1,8)` <br/>
(use `git checkout $commit$` if needed) 

[Back to the experiment page]({% post_url 2014-12-09-experiment-2-10k-agents-slash-100-generations %})

## Basic Statistics:
These very roughly characterize what kind of data structure we get out of simulation.

```{r groovy-basic, engine='groovy', echo=FALSE}
def env = System.getenv()
dataDir = env['R_dataDir']
def analysisDataFile = dataDir+'/analysisDataTemp.dat'
Map analysisData = new ConfigSlurper('analysisData').parse(new File(analysisDataFile).toURI().toURL())

println "\nNUMBER OF VERTIXES:"
analysisData.vertexes.each{
  println it.key + "=" + it.value
}
println "\nNUMBER OF EDGES:"
analysisData.edges.each{
  println it.key + "=" + it.value
}

println "\nPERFORMANCE:"
def atomicEvents = 0
analysisData.edges.each{atomicEvents += it.key =="knowsLinks"?0:it.value.toInteger()}
println "Number of atomic events: "+ atomicEvents

def parametersFile = dataDir+'/parameters.conf'
Map params = new ConfigSlurper('parameters').parse(new File(parametersFile).toURI().toURL())
simulationStartSec = params.simulationStartWall * 1.0E-9
simulationFinishSec = params.simulationFinishWall * 1.0E-9
simulationTimeSec = simulationFinishSec - simulationStartSec
println "Total simulation time (secs): "+simulationTimeSec
println "Total simulation time (hours): "+simulationTimeSec/3600
averageTimePerEvent = simulationTimeSec / atomicEvents
print "Average time per atomic event (secs): "+averageTimePerEvent

```

## Average benefit:
```{r groovy-average, engine='groovy', echo=FALSE}
def env = System.getenv()
dataDir = env['R_dataDir']
def analysisDataFile = dataDir+'/analysisDataTemp.dat'
Map analysisData = new ConfigSlurper('analysisData').parse(new File(analysisDataFile).toURI().toURL())
println "\nAVERAGE TOTAL BENEFIT:"
println analysisData.averageBenefit
``` 

```{r plot-benefit, echo=FALSE}
source('/media/data/challprop-working/challprop-analytics/R/average_benefit.R')
averageBenefit
```

## Average benefit change per unit of time:
```{r plot-benefit-per-time, echo=FALSE}
averageBenefitPerUnitOfTime
```

## Discussion


[Back to the experiment page]({% post_url 2014-12-09-experiment-2-10k-agents-slash-100-generations %})